\documentclass[12pt, a4paper]{report} % Use 'report' for longer documents like theses

\usepackage[utf8]{inputenc} % For UTF-8 character encoding
\usepackage{amsmath, amssymb} % For mathematical symbols
\usepackage{graphicx} % To include images
\usepackage{geometry} % To adjust page margins
\usepackage{hyperref} % For hyperlinks in the document (useful for TOC, references, etc.)
\usepackage{biblatex} % For managing references
\usepackage{fancyhdr} % For custom headers/footers
\usepackage{array} % Optional, for advanced table features

% Set page margins
\geometry{top=1in, bottom=1in, left=1in, right=1in}

% Bibliography file
\addbibresource{references.bib}

\title{ADS THESIS}
\author{Leonardo Luz Fachel}
\date{\today} % Date

% Define custom header
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\thepage} % Left-aligned page number in header
\fancyhead[C]{Thesis Title} % Centered title in header

\begin{document}

% Title page
\maketitle

% Abstract
\begin{abstract}
This is the abstract of your thesis. It provides a brief overview of your work, your methodology, results, and conclusions.
\end{abstract}

% Acknowledgments
\chapter*{Acknowledgments}
I would like to thank...

% Table of Contents
\tableofcontents
\newpage

% List of Figures and Tables
\listoffigures
\listoftables
\newpage

% Lista de Abreviaturas e Silgas
% \newpage

% Chapters
\chapter{Introduction}
This chapter introduces the topic of the thesis. You would provide an overview of the research area, the problem you are addressing, and the objectives of your research.

\section{Motivation}
The motivation for this research is...

\section{Referencial Theórico}
The main research questions are...

\chapter{Trabalhos Correlatos}
This chapter reviews existing research in the area of information technology and other related fields.

\chapter{Estado da Arte}
\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|}
\hline
Ano & Projeto & Link \\ \hline
Row 1, Col 1 & Row 1, Col 2 & Row 1, Col 3 \\ \hline
Row 2, Col 1 & Row 2, Col 2 & Row 2, Col 3 \\ \hline
Row 3, Col 1 & Row 3, Col 2 & Row 3, Col 3 \\ \hline
\end{tabular}
\caption{Example Table}
\end{table}


\section{Topic 1}
Discussion on the first topic...

\chapter{Metodoligia}
This chapter describes the methods used to conduct your research.

\chapter{Desenvolvimento}
Explain how you collected your data...

\chapter{Conclusão}
Describe the methods used for analyzing the collected data...

\chapter{Referências}
This chapter presents the findings from your research.

% Appendices
\appendix
\chapter{Appendix Title}
Include any additional information, such as code or raw data, that supports your thesis.

\chapter{Another Appendix}
More details if necessary...

% Bibliography
\newpage
\printbibliography

\end{document}
